Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-01-24 manuscript/manuscript.Rmd
Update manuscript.Rmd

```{r shifted-distributions, echo=FALSE, fig.cap=cap}
cap <- paste0(
  "Power transformations modified to be shift-sensitive produce transformation parameters that are invariant to location.")

@@

.create_density_plot <- function(x, plot_theme){
  p <- ggplot2::ggplot(
    data = data.table::data.table("x"=x),
    mapping = ggplot2::aes(
      x = x))
  p <- p + plot_theme
  p <- p + ggplot2::geom_density()
  p <- p + ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    panel.grid = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank())

@@

# Density
p_dens_normal <- .create_density_plot(
  x=x,
  plot_theme=plot_theme)

@@

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data_normal[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))
p_yj_normal <- p_yj_normal + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_normal <- p_yj_normal + ggplot2::theme(
  axis.title.y = ggplot2::element_blank(),
  axis.text.y = ggplot2::element_blank())

@@

# Density
p_dens_right <- .create_density_plot(
  x = x_right_skewed,
  plot_theme = plot_theme)

@@

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data_right[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))
p_yj_right <- p_yj_right + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
p_yj_right <- p_yj_right + ggplot2::theme(
  axis.title.y=ggplot2::element_blank(),
  axis.text.y=ggplot2::element_blank())

@@

# Density
p_dens_left <- .create_density_plot(
  x = x_left_skewed,
  plot_theme = plot_theme)

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data_left[method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_bc_left <- p_bc_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_bc_left <- p_bc_left + ggplot2::scale_shape_discrete(guide="none")

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data_left[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_yj_left <- p_yj_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_left <- p_yj_left + ggplot2::theme(
  axis.title.y=ggplot2::element_blank(),
  axis.text.y=ggplot2::element_blank())

@@

p <- egg::ggarrange(
  plots=list(
    p_dens_normal, p_bc_normal, p_yj_normal,
    p_dens_right, p_bc_right, p_yj_right,
    p_dens_left, p_bc_left, p_yj_left),
  ncol=3,
  draw=FALSE)
p
```

>>>>

```{r shifted-distributions, echo=FALSE, fig.cap=cap}
cap <- paste0(
  "Power transformations modified to be shift-sensitive produce transformation parameters are invariant to location.")

@@

.create_density_plot <- function(x, plot_theme){
  p <- ggplot2::ggplot(
    data = data.table::data.table("x"=x),
    mapping = ggplot2::aes(
      x = x))
  p <- p + plot_theme
  p <- p + ggplot2::geom_density()
  p <- p + ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    panel.grid = ggplot2::element_blank(),
    panel.border = ggplot2::element_blank())
  p <- p + ggplot2::xlim(c(-5, 5))

@@

# Density
p_dens_normal <- .create_density_plot(
  x=x,
  plot_theme=plot_theme)
p_dens_normal <- p_dens_normal + ggplot2::ggtitle(label="normal distribution")
p_dens_normal <- p_dens_normal + ggplot2::theme(plot.title=ggplot2::element_text(
  hjust=0.5,
  size=ggplot2::rel(1.0)))

@@

# Yeo-Johnson
p_yj_normal <- .create_lambda_shift_plot(
  data=data_normal[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-3.6, 1.1))
p_yj_normal <- p_yj_normal + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_normal <- p_yj_normal + ggplot2::scale_shape_discrete(guide="none")
# p_yj_normal <- p_yj_normal + ggplot2::theme(
#   axis.title.y = ggplot2::element_blank(),
#   axis.text.y = ggplot2::element_blank())

@@

# Density
p_dens_right <- .create_density_plot(
  x = x_right_skewed,
  plot_theme = plot_theme)
p_dens_right <- p_dens_right + ggplot2::ggtitle(label="right-skewed distribution")
p_dens_right <- p_dens_right + ggplot2::theme(plot.title=ggplot2::element_text(
  hjust=0.5,
  size=ggplot2::rel(1.0)))

@@

# Yeo-Johnson
p_yj_right <- .create_lambda_shift_plot(
  data = data_right[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(1.0, 65))
p_yj_right <- p_yj_right + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_right <- p_yj_right + ggplot2::scale_shape_discrete(guide="none")
# p_yj_right <- p_yj_right + paletteer::scale_color_paletteer_d(
#   palette = "ggthemes::Tableau_10",
#   drop = FALSE)
# p_yj_right <- p_yj_right + ggplot2::theme(
#   axis.title.y=ggplot2::element_blank(),
#   axis.text.y=ggplot2::element_blank())

@@

# Density
p_dens_left <- .create_density_plot(
  x = x_left_skewed,
  plot_theme = plot_theme)
p_dens_left <- p_dens_left + ggplot2::ggtitle(label="left-skewed distribution")
p_dens_left <- p_dens_left + ggplot2::theme(plot.title=ggplot2::element_text(
  hjust=0.5,
  size=ggplot2::rel(1.0)))

# Box-Cox
p_bc_left <- .create_lambda_shift_plot(
  data = data_left[method == "Box-Cox"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_bc_left <- p_bc_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE)
# p_bc_left <- p_bc_left + paletteer::scale_color_paletteer_d(
#   palette = "ggthemes::Tableau_10",
#   drop = FALSE,
#   guide = "none")
# p_bc_left <- p_bc_left + ggplot2::scale_shape_discrete(guide="none")

# Yeo-Johnson
p_yj_left <- .create_lambda_shift_plot(
  data = data_left[method == "Yeo-Johnson"],
  plot_theme = plot_theme,
  limits = c(-10.5, 0.5))
p_yj_left <- p_yj_left + paletteer::scale_color_paletteer_d(
  palette = "ggthemes::Tableau_10",
  drop = FALSE,
  guide = "none")
p_yj_left <- p_yj_left + ggplot2::scale_shape_discrete(guide="none")
# p_yj_left <- p_yj_left + ggplot2::theme(
#   axis.title.y=ggplot2::element_blank(),
#   axis.text.y=ggplot2::element_blank())

@@

p <- egg::ggarrange(
  plots=list(
    p_dens_normal, p_bc_normal, p_yj_normal,
    p_dens_right, p_bc_right, p_yj_right,
    p_dens_left, p_bc_left, p_yj_left),
  ncol=3,
  heights=c(0.5, 1.0, 1.0),
  byrow=FALSE,
  draw=FALSE)
p
```
